Data Analysis and Statistics

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Fixed broken links and section references caused by reorg

The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.

@@

* In cases where ratiometric data is not available, heat maps have been employed to display relative enrichment between conditions. 
  * For example, [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) reports only peptide spectral mapping counts. In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.

>>>>

The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/probevsprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.

@@

* In cases where ratiometric data is not available, heat maps have been employed to display relative enrichment between conditions. 
  * For example, [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) reports only peptide spectral mapping counts. In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/probevsprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.
